Efficient Community Formation \\ for Web Services

### 2014-01-01 papers/coalition-journal-R1/response_letterr.tex

\vspace{0.4cm}\textbf{\underline{4. Reviewer}:}
What do you mean by "the algorithm gets interrupted": is it based on
a logical condition? if yes, what is it?

\vspace{0.2cm}\textbf{\underline{Answer 4}:
It means if there is time constraint, the algorithm can get interrupted any time, and yet have depth(n-1) results. Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any loner,  we at least have checked for all subsets of depth 9}

\vspace{0.4cm}\textbf{\underline{5. Reviewer}:}
Please provide equations using lambda and epsilon and relate them
to your model that uses Rc.

\vspace{0.2cm}\textbf{\underline{Answer 5}:
We added the new stability($Core$ condition) in case of having taxtation.}

@@

\vspace{0.4cm}\textbf{\underline{5. Reviewer}:}
For the epslion core method: the value of epsilon should be
varied to verify its impact in the experiments section.

\vspace{0.2cm}\textbf{\underline{Answer 5}:
That is exactly what we are doing, we changes the explanation to make what we did more clear.}

\vspace{0.4cm}\textbf{\underline{6. Reviewer}:}
The experiments are missing a comparison with [18] is missing.

\vspace{0.2cm}\textbf{\underline{Answer 6}:
The expirement which was illustrated in figure[9] was comparision of our work with [18], for all the scenarios which we could make it comparable and fair with. We have called their method ``High Availability Coalition Method''}

@@

\newpage

\begin{center}
  \textbf{Reviewer 3}
\end{center}

\vspace{0.4cm}\textbf{\underline{1. Reviewer}:}  It is not convincing that the formation of service community can be modeled as a cooperative gaming problem. First, the concept of service community used in this paper is different from the ones used in the existing work, such as in the referred papers. The general idea of service community is a homogeneous service group that conceptually include services providing similar functionality. Services in the same community are independent and autonomous. There is no central control mechanism for the community. On the other hand, the concept of service community of this paper is a group of services which are monitored and managed by a community manager. It is not clear how realistic or practical such a community is and what the real world examples are.

\vspace{0.2cm}\textbf{\underline{Answer 1}: Most of the existing work such as [Liu 2012][18] (Coordinators), [Lim 2012][16] (Master Web Services], [Benatallah 2003][9] (Service Containers), [Maamar 2008][14], [Maamar 2009][8] (Master Web service), [Zeng 2003][11] (Service selection and task delegation), [Medjahed 2005][13] (Community Providers), [Limam 2010]\footnote{Managing Web Services Communities: A Cache for Queries Optimisation, International Journal on Web Service Computing, Vol.1, No.1, pp 2230-7702, 2010} (Centralized access in their community definition), have clearly stated that communities of web services need a centralized manager for the purposes of developing, coordinating and managing the community and in some of the works, being the access point of the community and having the task of delegating tasks.  We have added a web service community related work section to highlight this point.}

@@

\vspace{0.4cm}\textbf{\underline{2. Reviewer}:}  The problem is modeled in a way so that the cooperative game theory can be applied, but not in a way that is consistent with the real world scenarios. The service parameters, such as its request rate and throughout rate are not in line with the general characteristics of web services, such as input and output parameters. It is not clear how the proposed service parameters are obtained and why they are important to determine a service's membership to a community, considering that they depend on not only the service's capacity, but also the amount and frequency of user requests, which can be random.

\vspace{0.2cm}\textbf{\underline{Answer 2}: For web services quality metrics, we have used a real world data set provided at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/. Having a request rate for communities cannot be unrealistic, here is a real world example: Kooshiar Azimian. CEO of concertboom.com has provided me with their access and request rates of the web services they use\ref{cblog}. Their website provides ticketing information for events happening close to user's location. They use Ticketnetwork.com web services\footnote{Affiliate program link: http://www.ticketnetwork.com/affiliates/agreement.aspx} \footnote{Web Service API documentation: http://www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}, \footnote{We were asked not to enclose these data publicly, thats why we could not add them to paper} and have implemented their back-end code in Java. They currently almost have 340,000 daily page views, so they call the ticketnetwork web service almost 4 times per second to get the seating chart and tickets available for the events. During a day, the pick time happens at around 20:00 UTC time, which has almost 10\% more request rates than around the lower pick which is around 7:00 AM UTC time. Therefore basically ticketnetwork, knows concertboom.com as a user has a request rate of 340,000 requests per day or almost 3.95 requests per second and they can adjust and change these thresholds, and adjust the internal service providers and resources they have to provide these rate of services.
}

\begin{figure}
\begin{center}
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=10cm]{cb.eps}\label{cblog}
\caption{Number of ticket pageviews of concertboom.com during May 5th, until Sep 9th, 2013}
\end{center}
\end{figure}

@@

\vspace{0.4cm}\textbf{\underline{3. Reviewer}:}  The paper conducted a simulation instead of an experimental study using real world web services. This also suggests the difficulties of finding real world examples and application for the proposed idea.

\vspace{0.2cm}\textbf{\underline{Answer 3}: Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information. As mentioned in previous answer we used a real data set of web services (http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/) for our implementations. We also added a functional SOAP (xml) based request, response to our implementation, however this as expected did not affect our simulation results, since our concern, as most of the related work, in on non-functional properties of web services. We added a modification to paper and highlighted this. In many related work such as
[Yu 2013]\footnote{Q. Yu and A. Bouguettaya, Efficient Service Skyline Computation for Composite Service Selection, IEEE Transactions on Knowledge and Data Engineering (TKDE), vo. 25, no. 4, pp. 776-789, 2013},
[Limam 2010]\footnote{Managing Web Services Communities: A Cache for Queries Optimisation, International Journal on Web Service Computing, Vol.1, No.1, pp 2230-7702, 2010}, and
[Liu 2012]\footnote{A. Liu, Q. Li, L. Huang, S. Ying, and M. Xiao,Coalitional game for community-based autonomous web services cooperation, IEEE Transactions on Services Computing, vol. 99, no. PrePrints, 2012.}
the results have been evaluated using simulations}

@@

\vspace{0.4cm}

\vspace{1cm}

Finally, we hope that we have answered all the questions raised by
the reviewers, which will make the paper accepted for publication
in IEEE Transactions on Services Computing (TSC).

### 2014-01-01 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

Our algorithm works as follows. Given an established community
with a coordinator and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity of our game having characteristic function
where the new member is added. In this equation (i.e., Equation
\ref{eq:convex_snow}), let $C$ be our community members before the
new web service joins the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

The solution we propose for communities to ensure  stability is
applying a tax $\epsilon$, which is an amount of cost for those
web services that decide to change communities, which would make
deviation a costly act. However, this would require all the
community coordinators to agree on a same amount of taxation,
being governed by some external entities; otherwise, web services
would join communities charging the lowest amount of tax. Another
viable solution we introduce to our scenario is to stabilize the
game using external subsidies. The reason a game is not stable is
that the community is not making enough revenue to allocate enough
gain to the players. A community coordinator can subside its community
with a constant coefficient value of $\lambda$.
%
%Rewarding a community with high number of quality participants
%with $\lambda v(C)$, where $\lambda \leq 1$.
%
Obviously, with a big value for $\lambda$, it is always possible
to stabilize the community. However, this can be a costly act for
the community coordinators, so they are interested in the minimum
subside value of $\lambda$ making the community stable. Subsiding
or taxing in order to reduce the bargaining power of sub
coalitions are called $taxation$ \cite{eps346856} methods. We
evaluate the effectiveness of these two methods experimentally
through extensive simulations in the next section.

@@

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments. We created a pool of
web services and populated most of their \emph{QoS} parameters
from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented 
environment includes the QWS dataset by Eyhab Al-Masri and Qusay H. Mahmoud 
freely available at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. We implemented the simulations
using Java and executed the simulations on an Intel Xeon X3450
machine with 6GBs of memory. For other parameters missing from the
dataset, we used normal random distribution with parameters
estimated using the method of maximum likelihood.

>>>>

Our algorithm works as follows. Given an established community
with a coordinator and some member web services, a web service would
send a \emph{join request} to join  the community. Ideally, the
\emph{core} or \emph{$\epsilon$-core} stability of the group
having this new member should be analyzed. As the normal core
membership algorithm is computationally intractable, we exploit
Proposition \ref{proposition1} and Equation \ref{eq:convex_snow}
to check the convexity condition for our game considering the characteristic function 
when the new member is added. In this equation (i.e., Equation
\ref{eq:convex_snow}), let $C$ be our community members before the
new web service joins the community. Let  ${i}$ be the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

@@

The solution we propose for communities to ensure  stability is
applying a tax $\epsilon$, which is an amount of cost for those
web services that decide to change communities, which would make
deviation a costly act. However, this would require all the
community coordinators to agree on a same amount of taxation,
being governed by some external entities; otherwise, web services
would join communities charging the lowest amount of tax. Another
viable solution we introduce to our scenario is to stabilize the
game using external subsidies. The reason a game is not stable is
that the community is not making enough revenue to allocate enough
gain to the players. A community coordinator can subside its community
with a constant coefficient value of $\lambda$.
%
%Rewarding a community with high number of quality participants
%with $\lambda v(C)$, where $\lambda \leq 1$.
%
Obviously, with a big value for $\lambda$, it is always possible
to stabilize the community. However, this can be a costly act for
the community coordinators, so they are interested in the minimum
subside value of $\lambda$ making the community stable. When a new web service $i$, wants to join the community, the valuation function of the community members and the new web service is subsided by the community coordinator in order to incentivize formation of this community and is set to:
\begin{equation}\label{taxv}
v'(C \cup \{i\}) = \lambda \times v(C \cup \{i\})
\end{equation}
In equation \ref{eq:convex_snow} the value of $v'$ is replaced with the valuation function for the new forming coalition $C \cup \{i\}$.
Subsiding or taxing in order to reduce the bargaining power of sub
coalitions are called $taxation$ \cite{eps346856} methods. We
evaluate the effectiveness of these two methods experimentally
through extensive implementations in the next section.

@@

In this section, we discuss the experiments we performed for our
scenarios to validate the applicability and performance of our
proposed methods in realistic environments. We created a pool of
web services and populated most of their \emph{QoS} parameters
from a real world web service dataset
\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented 
environment includes the QWS dataset by Eyhab Al-Masri and Qusay H. Mahmoud 
freely available at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. We implemented the scenarios
using Java and executed the implementation on an Intel Xeon X3450
machine with 6GBs of memory. For other parameters missing from the
dataset, we used normal random distribution with parameters
estimated using the method of maximum likelihood.
